Proposed Solution

### 2017-04-18 OOPSLA17/secs/intro.tex
...

%what is the problem
Configuration errors (also known as misconfigurations) have become
one of the major causes of system failures, resulting in security vulnerabilities,
application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. 
In a recent high visible case~\cite{mashableNews},  
Facebook and Instagram became inaccessible
and a Facebook spokeswoman reported that 
this was caused by a change to the site's configuration systems.
In another case, a system configuration change caused an outage of AT\&T's 911 service for five hours.
During this time, 12,600 unique callers were not able to reach the 911 emergency line~\cite{att-outage}.
These critical system failures are not rare -
a software system failures study~\cite{yin11anempirical},
reports that about 31\% of system failures were caused by 
configuration errors.
This is even higher than the percentage of failures resulting from program bugs (20\%).

@@

%what do we do
In this paper, we propose a framework for automated verification of 
configuration files, which mimics standard automated verification 
techniques: for a given configuration file, we  checked if it 
adheres to a specification, and if there are issues we report them to 
the user.

@@

Our implementation, \app, detects errors that may cause total system failures, but can also find more insidious errors, for example configurations that will slow down the system only when the server load increases beyond a certain threshold.
Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging techniques~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.

@@

Our learning algorithm surmounts both of these shortcomings present in 
existing tools. \app implements a learning
algorithm inspired by association rule
learning~\cite{agrawal1993mining} that analyzes a training set of partially correct files.
A file in the training set might contain several different errors, but errors only appear 
in a small percentage of files. 
We first translate those file into an intermediary typed language.
\app then learns rules based on the inferred types of the keywords from the training set.
However, since the files might also contain errors we take 
this into account when learning correct rules. All learned rules are 
annotated with the probability of correctness.  
To ensure the learned rules are correct enough,
\app employs a graph analysis to refine the set learned rules.
\app analyzes the rule graph to rank the importance and relevance of the learned rules.

We have implemented a tool, \app, and evaluated it on almost 1000 real-
world configuration files from Github.
We demonstrate that we are able to detect known errors, based on 
StackOverflow posts, in this data set.
Furthermore, we find compelling evidence that out optimizations are 
effective
For example, we introduce a probabilistic type inference system that removes 1023 false 
positives errors reports to reduce the total error reports to 324.
The rule graph analysis drastically improves the ranking of importance of 
the error reports, which allows users to more quickly correct the most 
critical misconfigurations.
Additionally, \app scales linearly, whereas 
a previous tool~\cite{santolucitoCAV} showed exponential slow downs on 
the same benchmark set.

>>>>

%what is the problem
Configuration errors (also known as misconfigurations) have become
one of the major causes of system failures, resulting in security vulnerabilities,
application outages, and incorrect program executions~\cite{xu15systems, xu13do, xu15hey}. 
In a recent highly visible case~\cite{mashableNews},  
Facebook and Instagram became inaccessible
and a Facebook spokeswoman reported that 
this was caused by a change to the site's configuration systems.
In another case, a system configuration change caused an outage of AT\&T's 911 service for five hours.
During this time, 12,600 unique callers were not able to reach the 911 emergency line~\cite{att-outage}.
These critical system failures are not rare -
a software system failures study~\cite{yin11anempirical},
reports that about 31\% of system failures were caused by 
configuration errors.
This is even higher than the percentage of failures resulting from program bugs (20\%).

@@

%what do we do
In this paper, we propose a framework, \app, for automated verification of 
configuration files, which mimics standard automated verification 
techniques: for a given configuration file, we  checked if it 
adheres to a specification, and if there are issues we report them to 
the user.
Our framework surmounts both of the aforementioned shortcomings present in existing tools.

@@

\app detects errors that may cause total system failures, but can also find more insidious errors, for example configurations that will slow down the system only when the server load increases beyond a certain threshold.
Since these runtime errors may only be triggered after some time in a deployment environment, the standard debugging techniques~\cite{Zeller:2005:WPF:1077048} of starting a system multiple times with different configuration settings will not help detect these misconfigurations.

@@

\app works by analyzing a training set of partially correct files.
A file in the training set might contain several different errors, but errors only appear 
in a small percentage of files. 
We first translate those file into an intermediary typed language.
\app then learns rules based on the inferred types of the keywords from the training set.
However, since the files might also contain errors we take 
this into account when learning correct rules. All learned rules are 
annotated with the probability of correctness.  
To ensure the learned rules are correct enough,
\app employs a graph analysis to refine the set learned rules.
\app analyzes the rule graph to rank the importance and relevance of the learned rules.

We implemented \app in Haskell  and evaluated it on almost 1000 real-
world configuration files from Github.
We demonstrate that we are able to detect known errors, based on 
StackOverflow posts, in this data set.
Furthermore, we find compelling evidence that out optimizations are 
effective
For example, we introduce a probabilistic type inference system that removes 1023 false 
positives errors reports to reduce the total error reports to 324.
The rule graph analysis drastically improves the ranking of importance of 
the error reports, which allows users to more quickly correct the most 
critical misconfigurations.
Additionally, \app scales linearly, whereas 
a previous tool~\cite{santolucitoCAV} showed exponential slow downs on 
the same benchmark set.
